\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{microtype}
\usepackage{array}
\usepackage{multirow}
\usepackage{enumitem}
\usepackage[numbers,sort&compress]{natbib}
\usepackage[hidelinks]{hyperref}
\usepackage{xurl}
\usepackage{caption}
\usepackage{float}
\usepackage{longtable}

\hypersetup{
  pdftitle={The Replay-Point Cliff: Why Pooled Tiny Transformers Break Latent-Replay Assumptions at 16 KiB},
  pdfauthor={Subhajit Roy},
  pdfsubject={Persistent- and transient-memory accounting for patient-specific ECG adaptation},
  pdfkeywords={ECG, continual learning, latent replay, LoRA, TinyML, transient memory, patient-specific adaptation}
}

\graphicspath{{figures/}}
\setlength{\parskip}{0.35em}
\setlength{\parindent}{0pt}
\captionsetup{font=small}
\newcommand{\kib}{\,\mathrm{KiB}}
\newcommand{\bytes}{\,\mathrm{B}}
\newcommand{\macrof}{macro-F1}
% long compound terms in this paper are otherwise unbreakable and cause
% marginal overfull lines; give TeX explicit break points.
\hyphenation{mi-nor-i-ty-class-strength-ened re-play-plas-tic-ity
             per-sis-tent-state pa-tient-spe-cif-ic post-pool
             hard-ware-mo-ti-vat-ed re-pro-duc-i-bil-i-ty}

\title{\textbf{The Replay-Point Cliff: Why Pooled Tiny Transformers Break
Latent-Replay Assumptions at 16\,KiB}\\
\large Persistent- and Transient-Memory Accounting for Patient-Specific ECG
Adaptation}

\author{Subhajit Roy\\
\small Independent Researcher\\
\small \texttt{subhajitroy005@gmail.com}}

\date{\today}

\begin{document}
\maketitle

\begin{abstract}
Latent replay adapts an on-device classifier by storing exemplars from a frozen
feature layer, and the continual-learning literature treats the choice of that
layer as a graded compression trade-off. We show this assumption breaks in a
globally-pooled tiny transformer. In a 6{,}643-parameter ECG transformer,
replay compressibility is a \emph{step function}, not a curve: a 198-sample beat
expands to 1{,}056 token elements and an 8{,}448-element feed-forward tensor, and
global average pooling then contracts the representation to 16 elements in a
single step. Only \emph{post-pool} replay is storage-compressive; every
pre-pool tap costs essentially the raw beat. We call this the
\textbf{replay-point cliff}, and it is a structural property of pooled
transformer families, not of this dataset. Second, we account for adaptation
memory on \emph{two} axes rather than one. Persistent state---trainable
parameters, gradients, optimizer moments, and the replay buffer, which a device
must retain between steps---is analytically bounded at 16\,KiB. Peak
\emph{transient} state, the forward+backward working set the persistent budget
excludes, we model byte-exactly under three implementation regimes: it ranges
from a fraction of a KiB for post-pool head adaptation to tens of KiB for
raw-replay encoder adaptation, a $\sim$300$\times$ asymmetry on the axis prior
work assumes negligible. Third, matched ablations attribute the adaptation gain
to encoder \emph{plasticity} ($p = 0.005$), not to replay volume. Finally, over
all 21 patient-disjoint MIT--BIH DS2 records and five seeds (630 chronological
adaptation cells), with the metric, statistical unit, tests, effect size,
equivalence margin, and multiplicity family fixed in a pre-registered plan
before analysis, a rank-1 encoder low-rank adapter with tens of raw replay
samples raises per-patient \macrof{} from $0.666$ to $0.810$ and a rank-2 adapter
to $0.811$, each improving 16 of 21 patients against 12 for maximum head-only
replay. Both adaptation strategies \textbf{beat the frozen model} (Holm
$p \le 0.017$); their \emph{direct} comparison with maximum head-only replay is
inconclusive---neither superior after correction nor equivalent within a
pre-specified margin of $\delta = 0.02$ \macrof{} at this sample size (minimum
detectable effect $\approx 0.01$--$0.04$)---so the result is a bounded
\textbf{replay--plasticity allocation frontier} of competitive operating points,
not a single winner. This study is software-only: no hardware runtime, SRAM,
latency, or energy is measured.
\end{abstract}

\textbf{Keywords:} arrhythmia classification; continual learning;
electrocardiography; low-rank adaptation; patient-specific learning; replay;
TinyML; transformers.

\input{sections/01_introduction}
\input{sections/02_related_work}
\input{sections/03_problem_and_method}
\input{sections/04_experimental_protocol}
\input{sections/05_results}
\input{sections/06_discussion}
\input{sections/07_limitations}
\input{sections/08_conclusion}

\appendix
\input{sections/09_appendix}
\input{sections/10_embedded_appendix}

\input{sections/11_statements}

\input{references}

\end{document}
