\section*{Declarations}
\addcontentsline{toc}{section}{Declarations}

\paragraph{Corresponding author.} Subhajit Roy,
\texttt{subhajitroy005@gmail.com}.

\paragraph{Ethics.} This study used publicly available, de-identified
physiological databases distributed through PhysioNet
\cite{goldberger2000physiobank,moody2001impact,greenwald1990svdb} and did not
involve new human-subject recruitment or intervention. No ethical approval was
required.

\paragraph{Data availability.} All data are public: the MIT--BIH Arrhythmia
Database, the St.\ Petersburg INCART 12-lead Arrhythmia Database, and the
MIT--BIH Supraventricular Arrhythmia Database, all obtainable from PhysioNet.
The DS1/DS2 record partitions, the external inclusion and exclusion manifests,
the INCART record-to-subject map, and every derived summary CSV behind the
tables and figures are released with the code at the repository below.

\paragraph{Code availability.} The adaptation framework, the constrained
configuration generator, the memory-accounting module, the statistical
pipeline, and the figure and table generators are released together with the
run configurations, the random seeds, and the environment specification needed
to reproduce every number in this paper. Every published value is regenerated
from released artifacts by a single driver
(\texttt{scripts/reproduce\_paper.py}); no result is transcribed by hand.

\vspace{0.3em}
\noindent
\begin{tabular}{@{}ll@{}}
Repository & \url{https://github.com/subhajitroy005/BudgetCL-ECG} \\
Software release & \texttt{v1.0.0-arxiv} (annotated, immutable tag) \\
\end{tabular}

\vspace{0.3em}
\noindent
The annotated, immutable Git tag \texttt{v1.0.0-arxiv} is the primary software
identifier and resolves unambiguously to the exact release commit. The release
manifest records artifact checksums, configuration identifiers, environment
information, and the release tag.

\noindent
The DS1 source checkpoint these results adapt from is pinned by

\vspace{0.2em}
\noindent\hspace*{\fill}%
\texttt{SHA-256 a6d4eff14caa4404eb57dc5e\-b9ecfcb9e9d3f1a1bf907d6d147fb5611eb79fce}%
\hspace*{\fill}
\vspace{0.2em}

\noindent
so a reproduction can verify it is starting from the same model. Raw PhysioNet
recordings are not redistributed; the repository provides download scripts and
itemized inclusion/exclusion manifests instead.

\paragraph{Funding.} This work received no external funding.

\paragraph{Competing interests.} The author declares no competing interests.

\paragraph{Author contributions.} S.R.\ conceived the study, implemented the
framework and experiments, performed the analysis, and wrote the manuscript.

\paragraph{Use of AI assistance.} An AI coding assistant was used for software
implementation, for generating analysis and figure scripts, and for editorial
assistance during manuscript preparation. All experimental design decisions,
all claims, and all interpretations are the author's; every reported number is
produced by the released code from saved run artifacts, and the author has
verified the correspondence between the manuscript and those artifacts.
